`intRo`

### 2015-01-06 departmental-seminar/seminar-slides-markdown.Rmd
code highlighting

```{r, eval=FALSE, tidy=FALSE}
shinyServer(function(input, output, session) {
  ## Module info
  module_info <- read.table("modules/modules.txt", 
                            header = TRUE, sep=",")
  ## Modules
  types <- c("helper.R", "static.R", "observe.R", 
             "reactive.R", "output.R")
  modules_tosource <- file.path("modules", 
                                apply(expand.grid(
                                module_info$module, types)
                                , 1, paste, collapse = "/"))
  ## Source the modules
  for (mod in modules_tosource) { source(mod, local = TRUE) }
})
```

>>>>

```{r, eval=FALSE, tidy=FALSE}
shinyServer(function(input, output, session) {
  ## Module info
  module_info <- read.table("modules/modules.txt", 
                            header = TRUE, sep=",")
  ## Modules
  types <- c("helper.R", "static.R", "observe.R", 
             "reactive.R", "output.R")
  modules_tosource <- file.path("modules", 
                                apply(expand.grid(
                                module_info$module, types)
                                , 1, paste, collapse = "/"))
  ## Source the modules
  for (mod in modules_tosource) {
    ### <b>
    source(mod, local = TRUE) 
    ### </b>
  }
})
```
